\documentclass[12pt]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{amstext}

%===========================================================%
\begin{document}
\begin{center}

{\Large  {\bf STAT1301 Advanced Analysis of Scientific Data}}
\medskip

{\large {\bf Semester 2, 2025}}

\medskip

{\large {\bf Assignment 2}}


\end{center}

The due date/time is given on Blackboard.
Please submit your assignment on Blackboard.  


\begin{enumerate}
%---------------------------------------------------------------------
%Q1
\item In a game of dice, two fair dice are rolled and the payout $X$ is the product of the two dice outcomes.  

\begin{enumerate}
\item What is the probability mass function (pmf) of $X$? 
\hfill [3 marks]

% 
\item What is the expected value of $X$?
\hfill [3 marks]

%
\item What is the standard deviation of the payout? 
\hfill [4 marks]

\end{enumerate}

\vspace{0.5cm}

%---------------------------------------------------------------------
%Q2
\item A laboratory is studying the growth of algae in a controlled environment. The growth of algae is measured by the amount of biomass produced (in grams), which can be modelled by a random variable $X$ with probability density function (pdf)
\[
		f_X(x) = c \left(x^2 - 60x + 800\right) 
		\quad \text{for } 0<x<20,
\]
where $c$ is a constant. 


\begin{enumerate}
\item Find the value of $c$. 
\hfill [2 marks]

%
\item Find the cumulative distribution function (cdf) of $X$.  
\hfill [3 marks]

%
\item Find the expected value of $(X)$.  
\hfill [2 marks]

%
\item The laboratory equipment can only detect biomass that exceeds 2 grams (the minimum detectable amount). What is the probability that the biomass exceeds 10 grams, given that it is detectable?    
\hfill [3 marks]

\end{enumerate}

\vspace{0.5cm}

%---------------------------------------------------------------------
%Q3 
\item Each day, a quality control officer inspects a random sample of 25 products from the production line of a factory. The probability of a product passing inspection (being defect-free) is 0.25. If the product passes, the factory saves \$3 in repair costs. If the product fails, the factory incurs an additional \$1 cost for re-inspection after repair.
Let $X$ be the number of products that passes inspection on a given day, and $Y$ be the net savings for the factory on that day. 

\begin{enumerate}
\item State the distribution of $X$, including all its parameters.  
	\hfill [2 marks]

% 
\item What is the minimum sample size needed so that the probability of finding at least one defect-free product exceeds 99\%?   
	\hfill [3~marks]

% 
\item Calculate the expected value and variance of the factory's net savings.  
	\hfill [3 marks]

	%
\item What is the probability that the factory will save at least \$27 on a given day?  
	\hfill [2~marks]

\end{enumerate} 

\vspace{0.5cm}

%---------------------------------------------------------------------
%Q4
\item A storeroom in a warehouse maintains strict temperature control to ensure that sensitive materials are stored at optimal conditions. The temperature of the storeroom follows a normal distribution with mean $\mu$ and standard deviation $\sigma$ degrees Celsius ($^{\circ}$C). The storeroom has a temperature threshold of $8^\circ$C to avoid damaging the materials. 

You may use statistical tables to answer this question, then use \textsf{R} to verify your results.  

\begin{enumerate}
\item Suppose the storeroom temperature is adjusted so that $\mu = 7.5^\circ$C and $\sigma = 0.3^\circ$C. What is the probability that the temperature of the storeroom will be between $7.2^\circ$C and $8^\circ$C?
	\\\phantom{1} \hfill [3 marks]

% 
\item Assume that $\sigma=0.3^\circ$C. What should $\mu$ be set to so that the storeroom temperature exceeds $8^\circ$C only 1\% of the time? 
	\hfill [3 marks]
		
	%
\item What is the largest standard deviation $\sigma$ that will keep the temperature within $1^\circ$C of the mean with 95\% probability?
	\hfill [4 marks]	

\end{enumerate} 
\vspace{0.5cm}

%---------------------------------------------------------------------

\end{enumerate}


\end{document}
